Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
placeholders for remaining sections, will need to be majorly revised

% add footnote to legacysurvey website in section that compares
% wise depths in DECaLS DR1 versus DR2

@@

>>>>

It is important to quantify the effect of increased coverage on
the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
relative to those based on the AllWISE-only coadds of \cite{lang14}. A
full characterization should systematically explore a range of 
ecliptic and galactic latitudes, to consider the full spectrum of interplay
between decreased statistical noise and confusion. For isolated sources in the 
sky noise limit, we would expect a doubling of the W1/W2 imaging data
to increase the depth in each band by 0.38 mag.

The only existing catalogs based on our AllWISE+NEOWISER W1/W2 coadds
are forced photometry catalogs corresponding to DECam Legacy
Survey\footnote{http://legacysurvey.org} (DECaLS) DR2 optical sources. 
Optical sources from DECaLS DR1 are accompanied by forced based on the
\cite{lang14} W1/W2 coadds. Therefore, comparing the S/N of W1/W2
fluxes in DR2 versus DR1 allows us to obtain a preliminary estimate of the 
increased depths in regions of low ecliptic and high galactic latitude.

We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
higher S/N in W1 (W2). For comparison, the expectation based purely on
reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
S/N.

Much more work is needed to characterize the increased sensitivity
of WISE to faint sources due to the inclusion of NEOWISER
imaging, as this will inform forecasts about the final depths expected
upon WISE's permanent retirement.

@@

We have created a full-sky set of W1/W2 coadds which combine all publicly
available exposures from both the AllWISE and NEOWISER releases. Doubling the 
amount of WISE imaging relative to the AllWISE release has resulted in improved
W1/W2 depths and allowed for the elimination of nearly all time-dependent 
artifacts. Our new AllWISE+NEOWISER W1/W2 coadds are publicly available
via http://unwise.me.

Although the present analysis constituted a significant data processing 
endeavor, it represents only a small fraction of the work that must
be done to maximize science return from the NEOWISER imaging data set.
Creation of time-resolved coadds spanning the $\sim$5 year WISE-NEOWISER
time baseline would enable a wealth of important time-domain projects,
ranging from brown dwarf searches to quasar variability. As
additional years worth of NEOWISER data become publicly available, it
will be necessary to continue updating the full-depth WISE+NEOWISER coadds
to maximize the achieved depth. Finally, the creation WISE-only (as opposed
to forced photometry) catalogs based on deep coadds which include
NEOWISER images will be needed in order to enable a variety of exciting
discoveries.
